Proportional multi-state multiple-cohort life table model

### 2018-04-27 MSLT/MSLTdoc.Rmd
Multiple outputs in one page

#The work in this document requires the following packages (code, rmarkdown and citing packages):
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
require(gridExtra)
```

@@

i_outcome <- c("mx", "inc")

for (age in i_age_cohort){
  for (sex in i_sex) {
     for (disease in i_disease){
       for (outcome in i_outcome) {
         {
       if (sex == "male" && disease == "breast_cancer"){
         # cat("\n")
       }else{

 p <- plot_output(in_data = output_df, in_age = age, in_population = sex, in_outcomes = c("age", paste(outcome, "num", "bl", disease, sep = "_"), paste(outcome, "num", "sc", disease, sep = "_"), paste(outcome, "num", "diff", disease, sep = "_")), in_legend = paste(outcome, disease, sep = " "))
           }
         }
       }
     }
   }
 }

paste(age, sex, disease, outcome, sep = "_")

>>>>

#The work in this document requires the following packages (code, rmarkdown and citing packages):
require(dplyr)
require(tidyverse)
require(knitr)
require(kableExtra)
require(citr)
require(gridExtra)
require(cowplot)
```

@@

i_outcome <- c("mx", "inc")
p_list <- list()

index <- 1
for (age in i_age_cohort){
  for (sex in i_sex) {
     for (disease in i_disease){
       for (outcome in i_outcome) {
         {
       if (sex == "male" && disease == "breast_cancer"){
         # cat("\n")
       }else{
# names(p_list) <- unique(age, sex, disease, outcome)
 p_index  <- plot_output(in_data = output_df, in_age = age, in_population = sex, in_outcomes = c("age", paste(outcome, "num", "bl", disease, sep = "_"), paste(outcome, "num", "sc", disease, sep = "_"), paste(outcome, "num", "diff", disease, sep = "_")), in_legend = paste(outcome, disease, sep = " "))
p_list[[index]] <- p_index
index <- index + 1

            }
         }
       }
     }
   }
}

# m<-plot_grid(p_index, ncol=2, nrow=2)
# library(cowplot)
# save_plot("output.tiff",m ,ncol = 2, nrow = 2) # make room for figure legend)

# png(file="superplot.png")
# marrangeGrob(grobs=p_list, nrow=1, ncol=1)
# # do.call("grid.arrange", p_index)

ml <- do.call(marrangeGrob, list(grobs=p_list, nrow = 2, ncol = 2))
ml 
```
